Predicting the PCG Pseudo-Random Number Generator In Practice

### 2020-06-05 article/main.tex
version preprint

% !TeX spellcheck = en
\documentclass[submission,svgnames,journal=tosc]{iacrtrans}

@@

\author{Charles Bouillaguet\inst{1} \and Florette Martinez\inst{3} \and Julia Sauvage\inst{2}}

\institute{% 
University of Lille, France \\ 
\email{charles.bouillaguet@univ-lille.fr}
\and 
Sorbonne University \\
\email{julia.sauvage@etu.upmc.fr}
\and 
LIP6, CNRS, SU ? \\
\email{florette.martinez@lip6.fr}

}

@@

In this section, we briefly outline important aspects of our implementations and
present practical results. Our codes are available in the supplementary material
as well as online at:
\[
  % \url{https://github.com/cbouilla/pcg/}
  \verb|[----REDACTED FOR PEER REVIEW----]|
\]
The designer of \textsf{PCG} was kind enough to send us two sets challenge
inputs: one with the default (known) increment and one with a random secret
increment. She generated random seeds and provided us with the first outputs of
the pseudo-random generator. We were able to reconstruct the seed with an
extremely high confidence level, because they re-generate the same outputs. We
emailed back the seeds and received confirmation that they were indeed correct.

@@

It actually ran in 35 wall-clock minutes using 512 cluster nodes, each equipped
with two 20-cores \textsf{Intel Xeon Gold 6248 @ 2.5Ghz} (``\emph{Cascade
  Lake}''). The actual machine is the \verb|[----REDACTED----]| computer located
at the \verb|[----ALSO REDACTED----]| computation center. Note that on this
particular parallel computer, running the algorithm with $\ell=13$ would take 10
hours using the same amount of resources, so the whole procedure \emph{is}
practical, even in the absolute worst case.

@@

% pas dans la version anonyme.
% \paragraph{Acknowledgements.} The authors thank Damien Vergnaud and Vincent
% Zucca for helpful discussions. We also thank Léo Ducas for helping with the
% \texttt{G6K} library.

>>>>

% !TeX spellcheck = en
\documentclass[preprint,svgnames,journal=tosc]{iacrtrans}

@@

\author{Charles Bouillaguet\inst{1} \and Florette Martinez\inst{2} \and Julia Sauvage\inst{3}}

\institute{% ordre alphabétique
Univ. Lille, CNRS, Centrale Lille, UMR 9189 - CRIStAL - Centre de Recherche en Informatique Signal et Automatique de Lille, F-59000 Lille, France \\ 
\email{charles.bouillaguet@univ-lille.fr}
\and 
Sorbonne Université, CNRS, LIP6, F-75005 Paris, France \\
\email{florette.martinez@lip6.fr}
\and 
Sorbonne Université \\
\email{julia.sauvage@etu.upmc.fr}
}

@@

In this section, we briefly outline important aspects of our implementations and
present practical results. Our codes are available in the supplementary material
as well as online at:
\begin{center}
  \url{https://github.com/cbouilla/pcg/}
  %\verb|[----REDACTED FOR PEER REVIEW----]|
\end{center}
The designer of \textsf{PCG} was kind enough to send us two sets challenge
inputs: one with the default (known) increment and one with a random secret
increment. She generated random seeds and provided us with the first outputs of
the pseudo-random generator. We were able to reconstruct the seed with an
extremely high confidence level, because they re-generate the same outputs. We
emailed back the seeds and received confirmation that they were indeed correct.

@@

It actually ran in 35 wall-clock minutes using 512 cluster nodes, each equipped
with two 20-cores \textsf{Intel Xeon Gold 6248 @ 2.5Ghz} (``\emph{Cascade
  Lake}''). The actual machine is the \texttt{jean-zay} computer located at the
IDRIS national computation center. Note that on this particular parallel
computer, running the algorithm with $\ell=13$ would take 10 hours using the
same amount of resources, so the whole procedure \emph{is} practical, even in
the absolute worst case.

@@

% pas dans la version anonyme.
\paragraph{Acknowledgements.} The authors thank Thomas Espitau, Damien Vergnaud
and Vincent Zucca for helpful discussions. We also thank Léo Ducas for helping
us with the \texttt{G6K} library and Melissa O'Neil for kindly indulging our
request for challenge inputs.

This work was granted access to the HPC resources of IDRIS under the allocation
2019-A0060610749 made by GENCI.
